\huge \systemEnding: Growing Libraries of Concepts with Wake-Sleep Program Induction

### 2018-07-23 misc2.tex
More improvements to the poster.
poster stuff

s%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Portrait Poster
% LaTeX Template
% Version 1.0 (31/08/2015)
% (Based on Version 1.0 (29/03/13) of the landscape template
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% Portrait version by:
% John Hammersley
%
% The landscape version of this template was downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Kevin Ellis, Mathias Sabl\'e Meyer, Lucas Morales, Maxwell Nye, Luke Hewitt,\\ Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\begin{block}{Wake: Problem solving}
  \begin{tikzpicture}[scale=2.5,line width=1.3mm]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

    \node at ([xshift = 2cm]t) (nn){
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.4,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[align = center, text width = 1cm] at ([yshift = 0.6cm,xshift=-0.5cm]nn.north) {\baselineskip=0pt \small Recog. model\par};
    \draw [->] (t.east) -- ([xshift = -0.5cm]nn.west);

@@

    \draw [->] ([xshift = 0.5cm]nn.east) -- ([yshift = -0.25cm]s.west);
    \draw [->,rounded corners] (d.east) -- ([yshift = 2cm]nn.center) -- ([yshift = 0.25cm]s.west);

    \node[align=left] at (7,-1) (f) {Programs};
    \draw [->  ] (s.east) -- (f.west);

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}

@@

  %% Neural network
  %% predicts distribution over programs conditioned on tasks.
  %% Simple model: just predicts probabilities of DSL productions.  
  Goal: learn to invert generative model from (program, task) pairs

@@

  \textbf{Left column:} 16 out of 92 example tasks to hit in an all-or-none
  fashion --- training set for the \system algorithm.
  \textbf{Right column:} Learning curve for a run with a timeout of search time
  per task of 5 minutes (blue, bottom) and of 120 minutes (red, top). On the
  bottom are dreams, from left to right: before any training (original DSL, flat
  priors), at the end of the 5-minutes-timeout run, and at the end of the
  12-minutes-timeout run.

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
  The agent controls a `pen' on a 2D plant. Primitives are those of the LOGO
  language, modified to have a functional programing structure.
\end{column}
\end{columns}

@@

  We gratefully acknowledge collaboration with Eyal Dechter, whose EC algorithm (Dechter et al, IJCAI 2013) provided the inspiration for DreamCoder, and Luke Hewitt, who graciously provided us with
  a regex learning data set.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Portrait Poster
% LaTeX Template
% Version 1.0 (31/08/2015)
% (Based on Version 1.0 (29/03/13) of the landscape template
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% Portrait version by:
% John Hammersley
%
% The landscape version of this template was downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Kevin Ellis, Mathias Sabl\'e Meyer, Lucas Morales, %% Maxwell Nye, Luke Hewitt,
  \\ Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\begin{block}{Wake: Problem solving}
  \begin{tikzpicture}[scale=2.5,line width=1.3mm,arrowhead=0.1mm]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

    \node at ([xshift = 2cm]t) (nn){
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.4,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[align = center, text width = 1cm] at ([yshift = 0.6cm,xshift=-0.5cm]nn.north) {\baselineskip=0pt \small Recog. model\par};
    \draw [double,-{>[scale=0.2]}] (t.east) -- ([xshift = -0.5cm]nn.west);

@@

    \draw [double,->] ([xshift = 0.5cm]nn.east) -- ([yshift = -0.25cm]s.west);
    \draw [->,rounded corners,double,] (d.east) -- ([yshift = 2cm]nn.center) -- ([yshift = 0.25cm]s.west);

    \node[align=left] at (7,-1) (f) {Programs};
    \draw [double,->  ] (s.east) -- (f.west);

    \draw [->  ,rounded corners,double,] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}

@@

  %% Neural network
  %% predicts distribution over programs conditioned on tasks.
  %% Simple model: just predicts probabilities of DSL productions.  
  Goal: learn to invert generative model, trained on (program, task) pairs

@@

  \textbf{Left column:} 16 out of 92 example tasks %% to hit in an all-or-none
  %% fashion
 (training set). % for the \system algorithm.
  \textbf{Top right:} Learning curves for  runs w/ search timeout
    5 minutes (blue, bottom) and  120 minutes (red, top). \textbf{Bottom right:}
   dreams, from left to right: before learning, at the end of the 5-minute-timeout run, and at the end of the
  120-minute-timeout run. \textbf{Color gradient:} pen trajectory over time,
  %% aspect of the drawing part, or the pen,
  from blue (origin) to purple (end).

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
  Agent controls a `pen' on a 2 dimentional plane. LOGO/Turtle primitives.%% Primitives are those of
%% the LOGO language, modified to have a functional programing structure. Task
%%   don't take arguments (they are of type \texttt{unit -> image}) and the
%%   likelyhood function is all-or-none.

  Invented abstractions include:
  \begin{itemize}
    \item $\frac\pi2$ since it has $\pi$, $2$ and $/$ and needs right angles
    \item A line of any length followed with a right angle
    \item Loops of length $n$ that uses the number $n$ inside.
    \item A single line of unit length, followed by a set at the origin of the
      line
  \end{itemize}

  Deep embedding of invented abstractions: up to $7$, %observed level of embedding of invented primitives on the 2 hours
  %% run was $7$
  meaning that some invented primitives used invented and so on,
  seven times.

@@

  We gratefully acknowledge collaboration with Eyal Dechter, whose EC algorithm (Dechter et al, IJCAI 2013) provided the inspiration for DreamCoder.%% , and Luke Hewitt, who graciously provided us with
  %% a regex learning data set.
